Gozde and Liora Replication Code

### 2015-03-12 Gozde-Liora-Replication-Code.Rmd
ggplot figure added

for (i in 1:length(asy)) {
  j <- asy[i]
  se[i] <- deltamethod (~ (x17) + (x36)*j, estmean, var)
}

upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
asy.data <- cbind(asy, slopes, upper, lower)
plot(asy, slopes, type = "l", lty = 1, ylim=c(-.2, .2), xlim=c(-2, 4), ylab= "Effect: Unemployment", xlab = "Asylumseekers", main = "The Conditional Effects of Unemployment and Immigration")
points(asy, upper, type = "l", lty = 2)
points(asy, lower, type = "l", lty = 2)
points(asy, rep(0, length(asy)), type = "l", col = "black")
```

>>>>

for (i in 1:length(asy)) {
  j <- asy[i]
  se[i] <- deltamethod (~ (x17) + (x36)*j, estmean, var)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
asy.data <- cbind(asy, slopes, upper, lower)

# Creating the first graph in base R

plot(asy, slopes, type = "l", lty = 1, ylim=c(-.2, .2), xlim=c(-2, 4), ylab= "Effect: Unemployment", xlab = "Asylumseekers", main = "The Conditional Effects of Unemployment and Immigration")
points(asy, upper, type = "l", lty = 2)
points(asy, lower, type = "l", lty = 2)
points(asy, rep(0, length(asy)), type = "l", col = "black")

# Creating the same graph with ggplot - much better looking.

asy.data <- data.frame(asy.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Asylumseekers"
ytitle <- "Effect: Unemployment"
main <- "The Conditional Effects of Unemployment and Immigration"
ggplot(asy.data, aes(x=asy, y=slopes)) + 
  geom_line(aes(y=slopes), color="blue") + 
  geom_ribbon(aes(ymin=lower, ymax=upper), alpha=0.2) + 
  geom_hline(yintercept=0, size=0.4, color="black") +
  labs(x=xtitle, y=ytitle, title=main)
